Pomace: A Grappa for Non-Volatile Memory \vspace{-.2in}

### 2012-12-13 doc/nvm2013/paper.tex
spelling

\item [Tasking system.] Our tasking system supports lightweight
multithreading to tolerate communication latency; it also supports global distributed
workstealing (i.e., tasks can be stolen from any node in the system), which
provides automated load balancing.  Grappa thus tolerates many
microseconds of latency by multiplexing thousands of tasks per x86 core.

@@

\section{Applying non-volatile memory to Grappa}
The natural point of integration for non-volatile memories in Grappa
is to store the global distributed shared heap in nonvolatile memory, since for irregular applications the heap
often holds data that is infrequently modified. All accesses to
this shared heap in Grappa programs are done through an \textls*{\small API}, so this change could be made transparent to the programmer. 
If an 
access is to a chunk of the heap stored in a node's local memory, Grappa issues a prefetch for the address
and context switches to other work while the prefetch is executing~\cite{Nelson:hotpar2011}. If
the access is to memory stored on another node, Grappa issues a
message to that node requesting the data and context switches to other
work until the reply arrives. Non-volatile memory would be accessed in
the same way: If a request is to memory stored in non-volatile memory,
Grappa would initiate the request and context switch to other work
until the request had completed.

@@

For iterative applications where the entire graph is regularily
visited, an windowed approach similar to~\cite{graphchi:osdi12} may
provide more benefit. In this approach, graph data is constantly
streamed between \textls*{\small SSD} and \textls*{\small DRAM}. Requests wait to execute until the
relevant fragment of the graph is in memory. Request density is not a
concern for these applications; instead, bandwidth between the \textls*{\small SSD} and \textls*{\small DRAM}
is the limiting factor.

>>>>

\item [Tasking system.] Our tasking system supports lightweight
multithreading to tolerate communication latency; it also supports global distributed
work stealing (i.e., tasks can be stolen from any node in the system), which
provides automated load balancing.  Grappa thus tolerates many
microseconds of latency by multiplexing thousands of tasks per x86 core.

@@

\section{Applying non-volatile memory to Grappa}
The natural point of integration for non-volatile memories in Grappa
is to store the global distributed shared heap in non-volatile memory, since for irregular applications the heap
often holds data that is infrequently modified. All accesses to
this shared heap in Grappa programs are done through an \textls*{\small API}, so this change could be made transparent to the programmer. 
If an 
access is to a chunk of the heap stored in a node's local memory, Grappa issues a prefetch for the address
and context switches to other work while the prefetch is executing~\cite{Nelson:hotpar2011}. If
the access is to memory stored on another node, Grappa issues a
message to that node requesting the data and context switches to other
work until the reply arrives. Non-volatile memory would be accessed in
the same way: If a request is to memory stored in non-volatile memory,
Grappa would initiate the request and context switch to other work
until the request had completed.

@@

For iterative applications where the entire graph is regularly
visited, an windowed approach similar to~\cite{graphchi:osdi12} may
provide more benefit. In this approach, graph data is constantly
streamed between \textls*{\small SSD} and \textls*{\small DRAM}. Requests wait to execute until the
relevant fragment of the graph is in memory. Request density is not a
concern for these applications; instead, bandwidth between the \textls*{\small SSD} and \textls*{\small DRAM}
is the limiting factor.
